timesliced_random_cell_selection

### 2018-12-06 src/timesliced_random_cell_selection.Rmd
update to timesclice to remove cell removal process

ok so now I have a base list to work off... This gives you a dataset of xy points, but you need xyz (where z is based on the depth layers in the environmental data). This should be constrained by the presence depth range
```{r}
max_obs_depth <- max(mcpbase$depthlayerno, na.rm = TRUE) #max is 47
min_obs_depth <- min(mcpbase$depthlayerno, na.rm = TRUE) #min is 1
unique_cell_xyz <- mcp_unique_cell
unique_cell_xyz$depthlayerno <- NA
unique_cell_xyz <- unique_cell_xyz[rep(seq_len(nrow(unique_cell_xyz)), each=47),] #this generates 47  repetitions of each row 47 is chosen because there are 47 sampled depth layers
unique_cell_xyz$depthlayerno <- rep(1:47) #assign 1:47 on a repeating cycle to the depth column. 47 is chosen because there are 50 depth layers
unique_cell_xyz$id_depth <- paste(unique_cell_xyz$cell_id, unique_cell_xyz$depthlayerno, sep="") #create a new column that is a unique glo_unique_cell & depth ID. This is to help remove cells later and randomise
```

@@

Split the data_aea into timeslices (year/month).
All you need is the year, month, cell_id, and depthlayerno
```{r}
data_aea <- mcpbase
cell_yymm <- subset(data_aea, select= c(cell_id, depthlayerno, year, month)) #create a new df with just cell_id, yr, month, depthlayer no
cell_yymm$id_depth <- paste(cell_yymm$cell_id, cell_yymm$depthlayerno, sep="") #create a new column that is a unique cell_id & depth ID. This is to help remove cells later and randomise
split_cell_yymm <- split(cell_yymm, list(cell_yymm$year, cell_yymm$month), drop = TRUE)
```

>>>>

ok so now I have a base list to work off... This gives you a dataset of xy points, but you need xyz (where z is based on the depth layers in the environmental data). This should be constrained by the presence depth range
```{r}
max_obs_depth <- max(mcpbase$depthlayerno, na.rm = TRUE) #max is 47
min_obs_depth <- min(mcpbase$depthlayerno, na.rm = TRUE) #min is 1
unique_cell_xyz <- mcp_unique_cell
unique_cell_xyz$depthlayerno <- NA
unique_cell_xyz <- unique_cell_xyz[rep(seq_len(nrow(unique_cell_xyz)), each=47),] #this generates 47  repetitions of each row 47 is chosen because there are 47 sampled depth layers
unique_cell_xyz$depthlayerno <- rep(1:47) #assign 1:47 on a repeating cycle to the depth column. 47 is chosen because there are 50 depth layers
unique_cell_xyz$id_depth <- paste(unique_cell_xyz$cell_id, unique_cell_xyz$depthlayerno, sep="") #create a new column that is a unique glo_unique_cell & depth ID. This is to help remove cells later and randomise
write.csv(unique_cell_xyz, "../output/env/unique_cell_centroid_lonlat_nafo2_depth.csv", row.names = FALSE)
```

@@

Split the mcpbase into timeslices (year/month).
All you need is the year, month, cell_id, and depthlayerno
```{r}
cell_yymm <- subset(mcpbase, select= c(cell_id, depthlayerno, year, month)) #create a new df with just cell_id, yr, month, depthlayer no
cell_yymm$id_depth <- paste(cell_yymm$cell_id, cell_yymm$depthlayerno, sep="") #create a new column that is a unique cell_id & depth ID. This is to help remove cells later and randomise
split_cell_yymm <- split(cell_yymm, list(cell_yymm$year, cell_yymm$month), drop = TRUE)
```
